Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-01-28 joss/paper.Rmd
Edits
Renames script.long to script

```{R load-script, echo = FALSE, results = "hide"}
library(CodeDepends)
script <- system.file(
    "example", 
    "simple_script.R", 
    package = "Rclean")
script.long <- system.file(
    "example", 
    "long_script.R", 
    package = "Rclean")

@@

readLines(script.long)

@@

clean(script.long, "fit_sqrt_A")

>>>>

```{R load-script, echo = FALSE, results = "hide"}
library(CodeDepends)
script <- system.file(
    "example", 
    "simple_script.R", 
    package = "Rclean")
script.long <- system.file(
    "example", 
    "long_script.R", 
    package = "Rclean")
script <- script.long
```

@@

readLines(script)

@@

clean(script, "fit_sqrt_A")
